fl0w 2.0 - a development environment for the\\ KIPR Wallaby

### 2017-03-22 paper.tex
Update behem0ths protocol description.

@@

\subsubsection{Transfer}
behem0th neither sends nor receives files as a whole, instead it transmits the file size followed by data block which are written to a temporary file on disk. This is done to allow the transfer of files that are large enough to cause out of system memory situations.\\

\subsubsection{Protocol}
behem0th is independent from underg0und and defines its own network protocol. It also utilizes different routes nonetheless, which are directly perpended to the data segment, for file list transmission as well as actual date transfers.\\

@@

\begin{figure}[H]
\centering
	\begin{tabular}{*{2}{V}}
		Data size & (Route) Data \\ \hline
		4 & * \\
	\end{tabular}
	\caption{The binary encoding of behem0th (in bytes)}
\label{fig:behem0th_header}
\end{figure}

@@

@@

>>>>

% Define JSON language
\lstdefinelanguage{json}
{
morestring=[b]" % defines that strings are enclosed in double quotes
}

% JSON style for highlighting
\newcommand\jsonstyle{\lstset{
language=json,
basicstyle=\ttm,
stringstyle=\color{deepgreen},
frame=tb,
showstringspaces=false
}}

% JSON environment
\lstnewenvironment{json}[1][]
{
\jsonstyle
\lstset{#1}
}
{}

@@

\subsubsection{Transfer}
behem0th neither sends nor receives files as a whole, instead it transmits the file as small blocks (4096 bytes), which are written to a temporary file on disk as soon as they are received. This is done to allow the transfer of large files even in very memory-constrained environments.\\

\subsubsection{Protocol}
behem0th is independent from underg0und and defines its own network protocol. It is completely text-based, uses UTF-8\cite{UTF-8:F. Yergeau} for character encoding and JSON\cite{JSON:T. Bray Ed.} as format encoding. behem0th is designed around 'requests' $($see Figure ~\ref{fig:behem0th_request}$)$ and 'routes'. Each request is a JSON-formatted string and separated by a newline.

\begin{figure}[H]
\centering
\begin{json}
{
    "route": "<route-name>",
    "data": "<route-specific data>"
}
\end{json}
\caption{behem0th request}
\label{fig:behem0th_request}
\end{figure}

A route can also send additional data if needed (a 'payload'). For binary data, base64\cite{Base64:S. Josefsson} encoding is used. After the payload, there is again a newline to delimit payload and the next request. \\

@@

@@

\bibitem{UTF-8:F. Yergeau}
F. Yergeau, \emph{UTF-8}, \url{https://tools.ietf.org/html/rfc3629},\\ request for comment,
accessed March 22nd 2017

@@

\bibitem{Base64:S. Josefsson}
S. Josefsson, \emph{Base64}, \url{https://tools.ietf.org/html/rfc4648}, \\ request for comment,
accessed March 22nd 2017
